Locally Conservative Discontinuous Petrov-Galerkin Finite Elements for Fluid Problems

### 2013-02-26 docs/Truman/LocalConservation/paper.tex
Added figures for double glazing.

\documentclass[letterpaper]{article}
\usepackage[margin=1.0in]{geometry}
\usepackage{authblk}
\usepackage{amsmath, amssymb, amsthm, mathtools}
\usepackage{graphicx}
% \usepackage{subfigure}

@@

\begin{figure}[h!]
\centering
\parbox{0.45\textwidth}{
\includegraphics[width=0.45\textwidth]{figs/Erickson/graphError.pdf}
\caption{Error in Erickson-Johnson solution with graph norm}
\label{fig:ericksonGraphError}
}\quad
\parbox{0.45\textwidth}{
\includegraphics[width=0.45\textwidth]{figs/Erickson/robustError.pdf}
\caption{Error in Erickson-Johnson solution with robust norm}
\label{fig:ericksonRobustError}
}
\end{figure}

@@

\begin{figure}[h!]
\centering
\parbox{0.45\textwidth}{
\includegraphics[width=0.45\textwidth]{figs/Erickson/graphFlux.pdf}
\caption{Flux imbalance in Erickson-Johnson solutions with graph norm}
\label{fig:ericksonGraphFlux}
}\quad
\parbox{0.45\textwidth}{
\includegraphics[width=0.45\textwidth]{figs/Erickson/robustFlux.pdf}
\caption{Flux imbalance in Erickson-Johnson solutions with robust norm}
\label{fig:ericksonRobustFlux}
}
\end{figure}

@@

\begin{figure}[h!]
\centering
\parbox{0.45\textwidth}{
\includegraphics[width=0.45\textwidth]{figs/Confusion/graph0c.png}
\caption{Conservative skewed convection-diffusion with graph norm, initial mesh}
\label{fig:confusionGraph0c}
}\quad
\parbox{0.45\textwidth}{
\includegraphics[width=0.45\textwidth]{figs/Confusion/robust0c.png}
\caption{Conservative skewed convection-diffusion with robust norm, initial mesh}
\label{fig:confusionRobust0c}
}
\end{figure}

@@

% \begin{figure}[h!]
% \centering
% \parbox{0.45\textwidth}{
% \includegraphics[width=0.45\textwidth]{figs/Confusion/graph8nc.png}
% \caption{Nonconservative skewed convection-diffusion with graph norm, after 8
% refinements}
% \label{fig:confusionGraph8nc}
% }\quad
% \parbox{0.45\textwidth}{
% \includegraphics[width=0.45\textwidth]{figs/Confusion/robust8nc.png}
% \caption{Nonconservative skewed convection-diffusion with robust norm, after 8
% refinements}
% \label{fig:confusionRobust8nc}
% }
% \end{figure}

\begin{figure}[h!]
\centering
\parbox{0.45\textwidth}{
\includegraphics[width=0.45\textwidth]{figs/Confusion/graph8c.png}
\caption{Conservative skewed convection-diffusion with graph norm, after 8
refinements}
\label{fig:confusionGraph8c}
}\quad
\parbox{0.45\textwidth}{
\includegraphics[width=0.45\textwidth]{figs/Confusion/robust8c.png}
\caption{Conservative skewed convection-diffusion with robust norm, after 8
refinements}
\label{fig:confusionRobust8c}
}
\end{figure}

@@

\begin{figure}[h!]
\centering
\parbox{0.45\textwidth}{
\includegraphics[width=0.45\textwidth]{figs/Confusion/graphFlux.pdf}
\caption{Flux imbalance in skewed confusion solutions with graph norm}
\label{fig:confusionGraphFlux}
}\quad
\parbox{0.45\textwidth}{
\includegraphics[width=0.45\textwidth]{figs/Confusion/robustFlux.pdf}
\caption{Flux imbalance in skewed confusion solutions with robust norm}
\label{fig:confusionRobustFlux}
}
\end{figure}

>>>>

\documentclass[letterpaper]{article}
\usepackage[margin=1.0in]{geometry}
\usepackage{authblk}
\usepackage{amsmath, amssymb, amsthm, mathtools}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}

@@

\begin{figure}
\centering
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Erickson/graphError.pdf}
\caption{With graph norm}
\label{fig:ericksonGraphError}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Erickson/robustError.pdf}
\caption{With robust norm}
\label{fig:ericksonRobustError}
\end{subfigure}
\caption{Error in Erickson-Johnson solutions}
\end{figure}

@@

\begin{figure}
\centering
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Erickson/graphFlux.pdf}
\caption{With graph norm}
\label{fig:ericksonGraphFlux}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Erickson/robustFlux.pdf}
\caption{With robust norm}
\label{fig:ericksonRobustFlux}
\end{subfigure}
\caption{Flux imbalance in Erickson-Johnson solutions}
\end{figure}

@@

\begin{figure}
\centering
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Confusion/graph0c.png}
\caption{Conservative with graph norm}
\label{fig:confusionGraph0c}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Confusion/robust0c.png}
\caption{Conservative with robust norm}
\label{fig:confusionRobust0c}
\end{subfigure}
\caption{Skewed convection-diffusion problem with initial mesh}
\end{figure}

@@

\begin{figure}
\centering
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Confusion/graph8c.png}
\includegraphics[width=\textwidth]{figs/Confusion/graph8c_mesh.png}
\caption{Conservative with graph norm}
\label{fig:confusionGraph8c}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Confusion/robust8c.png}
\includegraphics[width=\textwidth]{figs/Confusion/robust8c_mesh.png}
\caption{Conservative with robust norm}
\label{fig:confusionRobust8c}
\end{subfigure}
\caption{Skewed convection-diffusion problem after 8 refinements}
\end{figure}

@@

\begin{figure}
\centering
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Confusion/graphFlux.pdf}
\caption{With graph norm}
\label{fig:confusionGraphFlux}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Confusion/robustFlux.pdf}
\caption{With robust norm}
\label{fig:confusionRobustFlux}
\end{subfigure}
\caption{Flux imbalance in skewed confusion solutions}
\end{figure}

\subsection{Double Glazing Problem}

\begin{figure}
\centering
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/DoubleGlazing/graph6c.png}
\caption{Conservative with graph norm}
\label{fig:doubleglazingGraph6c}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/DoubleGlazing/robust6c.png}
\caption{Conservative with robust norm}
\label{fig:doubleglazingRobust6c}
\end{subfigure}
\caption{Double glazing problem after 6 refinements}
\end{figure}

\begin{figure}
\centering
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/DoubleGlazing/graphFlux.pdf}
\caption{With graph norm}
\label{fig:doubleglazingGraphFlux}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/DoubleGlazing/robustFlux.pdf}
\caption{With robust norm}
\label{fig:doubleglazingRobustFlux}
\end{subfigure}
\caption{Flux imbalance in double glazing solutions}
\end{figure}
